% start of file `template.tex'.
%% Copyright 2006-2010 Xavier Danaux (xdanaux@gmail.com).
%% Copyright 2010-2011 Mark Liu (markwayneliu@gmail.com).
%% Copyright 2016-2017 Olga Botvinnik (olga.botvinnik@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[11pt,letterpaper,serif]{moderncv}

\usepackage{verbatim}

% moderncv themes
\moderncvstyle{classic}
\moderncvcolor{blue}
\frenchspacing
\usepackage{lastpage}

% character encoding
\usepackage[utf8]{inputenc}

% \usepackage[style=numeric-comp,
% sorting=none,defernumbers=true]{biblatex}%mod.
% \DeclareBibliographyCategory{cited}
% \AtEveryCitekey{\addtocategory{cited}{\thefield{entrykey}}}
% \addbibresource{publications.bib}

% adjust the page margins
\usepackage[scale=0.8]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
%\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

% --- Begin use with Multibib ----
\usepackage[resetlabels]{multibib}
%\usepackage[sorting=none]{multibib}
\newcites{book,article,poster}{{Books},{Journal Articles},{Conference Posters}}
% Number the Publications
\makeatletter
\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
\makeatother
\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}
% --- END use with Multibib ---

% BibTeX - don't print the year for publications that are "in press"
\newcommand{\dontprintyear}[1]{}


% personal data
\firstname{Lincoln J.}
\familyname{Harris}
\title{Curriculum Vitae}                        
\address{William H. Foege Hall}{3720 15th Ave NE}{Seattle, WA, 98195}
\email{lincolnh@uw.edu}                 
\social[github]{lincoln-harris}                             
\quote{Last Updated: \today}    

% to show numerical labels in the bibliography; only useful if you make citations in your resume
\makeatletter
\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
\makeatother

\begin{document}

\maketitle
\rfoot{\addressfont\itshape\textcolor{gray}{Page \thepage\ of \pageref{LastPage}}}

\cvline{}{Computational biologist with interests in machine learning, computational proteomics, scientific software development, outreach and open access science.}

\section{Education}
\cventry{2020-Present}{PhD, Genome Sciences}{University of Washington}{Seattle, WA}{}{Degree in progress.}
\cventry{2017}{B.A., Biology}{Swarthmore College}{Swarthmore, PA}{}{}

\section{Experience}

\cventry{2021-Present}{Bill Noble Laboratory}{University of Washington Department of Genome Sciences}{Seattle, WA}{}{
I utilize machine learning techniques to explore problems in computational proteomics. I frequently use cluster computing, \texttt{pytorch} , \texttt{scikit-learn}, and GPU-accelerated computing.   \\\\
Projects:
\begin{itemize}
    \item Imputation of quantitative mass spectrometry data with Non-negative Matrix Factorization and deep neural networks. 
\end{itemize}
}

\bigbreak

\cventry{2017--2020}{Chan Zuckerberg Biohub}{Spyros Darmanis Group}{San Francisco, CA}{Research Associate II}{
Investigated large biological datasets with a variety of tools including Docker, Python (\texttt{pandas, SciPy, Matplotlib, scikit-learn}), AWS, and workflow management systems such as NextFlow. Worked as part of a collaborative team in a fast-paced, cutting-edge scientific environment.  \\\\
Was promoted from Research Associate I to Research Associate II.   \\\\
Projects:
\begin{itemize}
\item Built a software tool for fast and memory-efficient summarizing of vcf (variant calling format) file entries following a sequencing experiment (\url{https://github.com/czbiohub/cerebra}.)
\item Identified variants in single-cell RNA-seq patient samples as part of a larger effort to better characterize changes in the lung tumor microenvironment across disease progression. In collaboration with the Trevor Bivona lab of UCSF.
\item Investigated the gene expression and alternate splicing dynamics of neuroendocrine cells in the developing lung, in collaboration with the Christin Kuo lab of Stanford.
\end{itemize}
}

\bigbreak

\cventry{2016--2017}{Brad Davidson Laboratory}{Swarthmore College Biology Department}{Swarthmore, PA}{}{
Assembled the genome and embryonic transcriptome of \emph{Corella Inflata} (sea squirt). Helped construct an improved phylogenetic tree for the \emph{Tunicate} subphylum, in collaboration with the Joe Ryan Lab of the University of Florida Whitney Marine Station
}

\section{Research Training}
\cventry{2020--2021}{Research Rotations}{University of Washington Department of Genome Sciences}{Seattle, WA}{}{Rotated in the labs of \href{https://sites.google.com/site/harriskelley/home}{Kelley Harris}, \href{https://www.beliveau.io/}{Brian Beliveau} and \href{https://noble.gs.washington.edu/}{Bill Noble}. Worked on population genetic simulations of extinction events, automatic annotation of cellular features from high-resolution microscopy images, and methods development for computational proteomics, respectively.}{}

\bigbreak

\cventry{2015}{Nick Kaplinsky Laboratory}{Swarthmore College Biology Department}{Swarthmore, PA}{}{Conducted basic plant molecular genetics research and learned basic lab skills such as western blotting, RNA extraction and PCR}{}

\section{Honors and Awards}
\cvline{2016 -- 2019}{Sigma Xi National Science Honors Society}

\section{Publications}
% --- START for use with multibib package ----
% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}          % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}        % 'publications' is the name of a BibTeX file

\renewcommand{\refname}{Articles}
\nocite{*}
%\bibliographystyle{plain}
\bibliographystyle{unsrt}
\bibliography{publications}          % 'publications' is the name of a BibTeX file
\bigbreak

\renewcommand{\refname}{Posters}
\nociteposter{*}
%\bibliographystyleposter{habbrvyrolgabold}
%\bibliographystyleposter{plain}
\bibliographystyleposter{unsrt}
\bibliographyposter{posters}                   % 'posters' is the name of a BibTeX file

% --- END for use with multibib package ----

\section{Talks}
\cvline{}{* indicates invited talk}

\cventry{2020-2021}{Graduate Student Rotation Talks}{University of Washington Department of Genome Sciences}{Seattle, WA}{}{Conducted three 10 min talks to culminate my first year rotations in the labs of Dr.s Kelley Harris, Brian Beliveau and Bill Noble.}{}
\bigbreak

\cventry{2019}{New methods for high-throughput variant call processing}{Beyond the Cell Atlas Conference}{Berkeley, CA*}{}{Was chosen as one of 15 speakers to present research at a selective single-cell transcriptomics conference attended by PIs and researchers from across the country.}{}
\bigbreak

\cventry{2019}{Single-cell characterization of cancer hallmarks in advanced stage Lung Adenocarcinoma}{Chan Zuckerberg Biohub Inter-lab Confab}{UCSF, San Francisco, CA}{}{}

\cventry{2017}{The genome and embryonic transcriptome of \emph{Corella Inflata}}{Undergraduate Biology Department Research Symposium}{Swarthmore College}{Swarthmore, PA}{}{}

\section{Software}

\cvline{\texttt{cerebra}}{Performs high-throughput summarizing of vcf entries following a sequencing experiment. 
\newline\url{https://github.com/czbiohub/cerebra} (51 stars on GitHub)}

\section{Leadership and Outreach}

\cventry{2021-Present}{Instructor}{The Carpentries Organization}{}{}{Certified to lead Data and Software Carpentries workshops designed to provide scientists with coding and data analysis skills}{}
\cventry{2021-Present}{Student Representative}{Graduate Council}{University of Washington Department of Genome Sciences}{Seattle, WA}{Attended monthly faculty meetings as the co-representative for graduate student interests.}{}
\cventry{2021-Present}{Volunteer}{Skype-A-Scientist}{}{}{Taught three basic science lessons for an elementary school classroom in Chicago, IL.}{}
\cventry{2021-Present}{Volunteer}{University of Washington Science Explorers}{Seattle, WA}{}{Organized, planned and led several basic science lessons for a local elementary school classroom.}{}
\cventry{2021-Present}{Member}{University of Washington Graduate Student Union}{Seattle, WA}{}{Attend student-led collective bargaining sessions and labor dispute demonstrations.}{}
\cventry{2017--2020}{Instructor}{Cupcakes and Coding}{Chan Zuckerberg Biohub}{San Francisco, CA}{Volunteered as an instructor at weekly beginner-friendly coding sessions}{}
\cventry{2013--2017}{Member}{Swarthmore College Swim Team}{Swarthmore, PA}{}{Participated as a four-year varsity member on a Division III swim team}{}

\section{Mentees}

\cventry{2019}{Rohan Vanheusden}{Nueva High School}{San Mateo, CA}{High School Student}{Mentored a local high school student with interests in computational biology for 11 weeks. }

\end{document}